### 2016-08-03 ms/ms.tex
added figures to ms

\def\runninghead{Coevolution and network structure}
\def\keywords{evolution, nestedness, modularity, bipartite}

@@

\begin{abstract}
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network disassembly,
  therefore, is a priority for system-level conservation biology.  We
  explore the assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. The assembling
  communities are paired with unrestored field margins (controls) and
  mature (non-assembling) hedgerows. We determine whether there are
  change points in the assembly of the communities where the network
  undergoes significant reorganization. We are also ask how are the
  individual species changing their interaction patterns? What does
  this mean for the topology/resilience of the network? We also
  attempted to adapt a financial model to mutualistic networks. Our
  biggest difficulty with this approach was to translate the price
  term to mutualistic systems. We explored a range of approaches, such
  as number of visits a species performs. However, it seems that
  financial systems cannot be easily translated to mutualistic
  systems. In addition, we used a Changing Point Detection Algorithm
  to assess weather the different communities went through a critical
  reorganization on their interaction patterns. We were able to
  identify some changing points in the communities, and also to
  explore some general patterns commonly used to describe ecological
  networks. For example, on the network level, networks become
  increasingly modular and less nested, whereas on the species level,
  species become more specialized, as resources become more reliable.
\end{abstract}

@@

\subsection*{Change point analysis}

We employed a change point detection method \citep{peel2014detecting}
to identify fundamental changes in large-scale pattern of interactions
of plants and pollinators. A change point is caused by a merge, split,
fragmentation or formation of communities (also called modules or
compartments). Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E \subseteq {V × V
}$. The GHRG model decomposes the $N$ vertices into a series of nested
groups, the relationships among which are represented by the
dendrogram $T$.  The tips of $T$ are the vertices of $G$, and the
probability that two vertices $u$ and $v$ connect is given by the
parameter $p_r$. The probability distribution of the network $G$ thus
defined as:

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed the reorganization of
interactions. To do so, we first generate dendrograms using the GHRG
model before and after each change point.  We then determined which
species belonged to the ``core'' and ``peripheral'' network
communities at each site. The ``core'' network communities contain the
majority of species and are more basil than the more derived, less
specious ``peripheral'' network communities. We next use a
Permutational Multivariate Analysis of Variance (PERMANOVA)
\citep{anderson-2013-557} to determine whether the species
compositions of the species that belonged to the core and peripheral
communities differed. We also test whether core or peripheral species
had more variability in their species compositions \citep[i.e.,
multivariate dispersion, ][]{anderson-2011-19,
  anderson-2006-683}.

@@

\section*{Results}
\label{sec:results}

>>>>

\def\runninghead{Plant-pollinator network assembly}
\def\keywords{community assembly, change points, specialization,
  nestedness, modularity, bipartite, preferential attachment}

@@

\begin{abstract}
TO BE RE-WRITTEN
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network disassembly,
  therefore, is a priority for system-level conservation biology.  We
  explore the assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. The assembling
  communities are paired with unrestored field margins (controls) and
  mature (non-assembling) hedgerows. We determine whether there are
  change points in the assembly of the communities where the network
  undergoes significant reorganization. We are also ask how are the
  individual species changing their interaction patterns? What does
  this mean for the topology/resilience of the network? We also
  attempted to adapt a financial model to mutualistic networks. Our
  biggest difficulty with this approach was to translate the price
  term to mutualistic systems. We explored a range of approaches, such
  as number of visits a species performs. However, it seems that
  financial systems cannot be easily translated to mutualistic
  systems. In addition, we used a Changing Point Detection Algorithm
  to assess weather the different communities went through a critical
  reorganization on their interaction patterns. We were able to
  identify some changing points in the communities, and also to
  explore some general patterns commonly used to describe ecological
  networks. For example, on the network level, networks become
  increasingly modular and less nested, whereas on the species level,
  species become more specialized, as resources become more reliable.
\end{abstract}

@@

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental changes in large-scale pattern of interactions
of plants and pollinators. A change point is caused by a merge, split,
fragmentation or formation of communities (also called modules or
compartments). Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E \subseteq {V × V
}$. The GHRG model decomposes the $N$ vertices into a series of nested
groups, the relationships among which are represented by the
dendrogram $T$.  The tips of $T$ are the vertices of $G$, and the
probability that two vertices $u$ and $v$ connect is given by the
parameter $p_r$. The probability distribution of the network $G$ thus
defined as:

@@

\subsubsection*{Characteristics of ``core'' and ``peripheral'' communities}
To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed the reorganization of
interactions. To do so, we first generate dendrograms using the GHRG
model before and after each change point.  We then determined which
species belonged to the ``core'' and ``peripheral'' network
communities at each site. The ``core'' network communities contain the
majority of species and are more basil than the more derived, less
specious ``peripheral'' network communities. We next use a
Permutational Multivariate Analysis of Variance (PERMANOVA)
\citep{anderson-2013-557} to determine whether the species
compositions of the species that belonged to the core and peripheral
communities differed. We also test whether core or peripheral species
had more variability in their species compositions \citep[i.e.,
multivariate dispersion, ][]{anderson-2011-19,
  anderson-2006-683}.

@@

\section*{Results}
\label{sec:results}
\subsection*{Change point analysis}
\subsubsection*{Identifying change points}

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{XXX}
  \label{fig:changePoints}
\end{figure}
\clearpage

\subsubsection*{Characteristics of ``core'' and ``peripheral''
  communities}

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/communities.pdf}
  \caption{XXX}
  \label{fig:communities}
\end{figure}
\clearpage

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/changePoint/plotting/figures/pcoa/pcoa.pdf}
  \caption{XXX}
  \label{fig:pcoa}
\end{figure}
\clearpage

\begin{figure}
  \centering
  \includegraphics[width=.4\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{XXX}
  \label{fig:baci}
\end{figure}
\clearpage

\subsection*{Network robustness}

%% no need for robustness figs bec not sig
